Stochastic Wind Power Forecasting

### 2020-02-03 LaTeX_code/paper/paper_1line.tex
last version added

Nevertheless, closed-form solutions to this initial-boundary value problem can be obtained only in a few cases. Besides, solving numerically (\ref{eq:fpk}) at every transition step is computationally expensive. 
Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations.

\subsection{Approximate Likelihood}
Solving for transition densities of the process $V_t$ requires solving the Fokker-Planck equation at every step which is computationally prohibitive. A common choice is performing a Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints which give rise to asymmetric forecasting errors as seen in figure (\ref{fig:skew_data}).\\

>>>>

Closed-form solutions to initial-boundary value problem for SDEs can be obtained only in a few cases. Besides, in our case solving numerically (\ref{eq:fpk}) for the transition densities of the process $V$ at every transition step is computationally expensive. 
Therefore, under the likelihood-based inferential paradigma, many techniques have been devised to obtain approximate maximum likelihood estimates for the unknown parameters of continuous-time SDE models with discrete observations. Parametric estimation problems for diffusion processes sampled at discrete times are presented in \autocite[Chapter 3]{iacus1}, and a survey of estimation methods for the parameter vector of the general one-dimensional, time-homogeneous SDE from a single sample of observations at discrete times is presented in \autocite{hurn}.

\subsection{Approximate Likelihood}

A common choice is performing a Gaussian approximation of the transition densities, but this is inappropriate here due to physical constraints which give rise to asymmetric forecasting errors as seen in figure (\ref{fig:skew_data}).\\
